FoRTE baseline

### 2019-10-01 analysis/paper/paper.Rmd
Add methods note about MS vs. 2S model
Minor tweaks to methods text

Both canopy radiative transfer models in ED-2.2 resolve the full vertical radiation profile within a patch as a function of canopy structure (leaf and wood area indices, crown area, leaf angle distribution) and incident solar radiation, following the definitions in CLM 4.5 [@clm45_note].
Both models also use identical definitions for the optical properties of a single canopy layer as a function of leaf and wood optical properties, leaf angle distribution, canopy clumping, solar zenith angle, and leaf, wood, and crown area indices.
Both models represent direct (a.k.a. "beam") radiation as an exponentially decaying process, and solve for the diffuse (a.k.a. "hemispherical", "isotropic") radiation at each layer using a linear matrix equation.
Where the models differ is in the terms of this matrix equation.
The two-stream model (default) uses the two-stream approximation originally derived for atmospheric radiative transfer [@meador_1980_two] and later adapted to vegetation canopies [@dickinson_1983_land; @sellers_1985_canopy].
Meanwhile, the multiple-scatter model was derived from first principles by @zhao_2005_multiple specifically for vegetation canopies, specifically to address known biases and limitations of the two-stream approach [e.g. @wang_2003_comparison].
Both of these models are described in detail in the Supplementary Information. <!-- TODO Exact reference to Appendix -->

The crown area submodel in ED-2.2 determines the nature of competition for light between cohorts.
In the default configuration ("infinite crown area", or "complete shading"), the leaf area of a cohort is distributed across the entire horizontal area of a patch.
This means that taller cohorts always receive more incoming radiation than shorter cohorts, even when the height difference is small.
This has been shown to excessively suppress competition from sub-dominant individuals and result in unrealistically homogeneous canopies [@fisher_2015_taking].
In the alternate configuration ("finite crown area", or "partial shading"), canopies take up only a fraction of the available horizontal area, meaning that multiple cohorts of similar height can receive the same level of light.
The horizontal area of crowns is determined by allometric equations from @dietze_2008_changing.

>>>>

Both canopy radiative transfer models in ED-2.2 resolve the full vertical radiation profile within a patch as a function of canopy structure (leaf and wood area indices, crown area, leaf angle distribution) and incident solar radiation, following the definitions in CLM 4.5 [@clm45_note].
Both models also use identical definitions for the optical properties of a single canopy layer as a function of leaf and wood optical properties, leaf angle distribution, canopy clumping, solar zenith angle, and leaf, wood, and crown area indices.
Both models represent direct (a.k.a. "beam") radiation as an exponentially decaying process, and solve for the diffuse (a.k.a. "hemispherical", "isotropic") radiation at each layer using a linear matrix equation.
Where the models differ is in the terms of this matrix equation.
The two-stream model (default) uses the two-stream approximation originally derived for atmospheric radiative transfer [@meador_1980_two] and later adapted to vegetation canopies [@dickinson_1983_land; @sellers_1985_canopy].
Meanwhile, the multiple-scatter model was derived from first principles by @zhao_2005_multiple specifically for vegetation canopies, specifically to address known biases and limitations of the two-stream approach [e.g. @wang_2003_comparison].
**Compared to the default two-stream model, the multiple-scatter model slightly increases diffuse light levels in the understory.**
Both of these models are described in detail in the Supplementary Information. <!-- TODO Exact reference to Appendix -->

The crown area submodel in ED-2.2 determines the nature of competition for light between cohorts.
In the default configuration ("infinite crown area", or "complete shading"), the leaf area of a cohort is distributed across the entire horizontal area of a patch.
This means that taller cohorts always receive more incoming radiation than shorter cohorts, even when the height difference is small.
This has been shown to excessively suppress competition from sub-dominant individuals and result in unrealistically homogeneous canopies [@fisher_2015_taking].
In the alternate configuration ("finite crown area", or "partial shading"), canopies take up only a fraction of the available horizontal area, which generally exposes the understory to more light.
The horizontal area of crowns is determined by allometric equations from @dietze_2008_changing.
